Data Archiving Attitudes

### 2018-03-20 manuscript.Rmd
fix label ordering, and make stacked bars

# unique(d$PolicyAdoptedAtPublication)
# d$label_PolicyAdoptedAtPublication <- ordered(d$PolicyAdoptedAtPublication, levels=c("No\nJDAP", "Before\nJDAP", "After\nJDAP"))
d$label_PolicyAdoptedAtPublication <- ordered(gsub(" ","\n",d$PolicyAdoptedAtPublication), levels=gsub(" ","\n",levels_TimeClass))

@@

library(ggplot2)
library(reshape2)
source("./src/aux_functions.R")
source("./src/plotLikert.R")

@@

responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
tmp <- melt(d, measure.vars=paste0('Q_4_',1:16 ))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
tmp <- melt(d_with_data, measure.vars=paste0('Q_4_',1:16 ))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

p <- ggplot(tmp, aes(label_PolicyAdoptedAtPublication, class.Proportion*100, group=value, fill=value))+geom_bar(stat="identity", position="dodge")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")
p + theme_bw()

@@

tmp <- melt(d, measure.vars=c('Q_9'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

@@

responses <- c("Strongly Agree","Strongly Disagree") # response categories from top to bottom
tmp <- melt(d, measure.vars=paste0('Q_10_',1:11 ))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("10_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("11_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='PolicyAdoptedAtPublication', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

>>>>

# unique(d$PolicyAdoptedAtPublication)
# d$label_PolicyAdoptedAtPublication <- ordered(d$PolicyAdoptedAtPublication, levels=c("No\nJDAP", "Before\nJDAP", "After\nJDAP"))
d$label_PolicyAdoptedAtPublication <- ordered(gsub(" ","\n",d$PolicyAdoptedAtPublication), levels=gsub(" ","\n",levels_TimeClass))
d$label_PolicyAdoptedAtPublication_space <- ordered(gsub(" "," ",d$PolicyAdoptedAtPublication), levels=gsub(" "," ", levels_TimeClass))

@@

library(dplyr)
library(ggplot2)
library(reshape2)
source("./src/aux_functions.R")
source("./src/plotLikert.R")

@@

responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
tmp <- melt(d, measure.vars=paste0('Q_4_',1:16 ))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

responses <- c( "Many times","A few times","Once","Never") # response categories from top to bottom
tmp <- melt(d_with_data, measure.vars=paste0('Q_4_',1:16 ))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("4_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Once", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

p <- ggplot(tmp, aes(x = label_PolicyAdoptedAtPublication, y = 100*class.Proportion, fill = value)) + geom_bar(stat = "identity")+xlab("JDAP Policy")+ylab("Proportion of responses (in %)")

p + theme_bw()

@@

tmp <- melt(d, measure.vars=c('Q_9'))
tmp$variable <- gsub("Q_", "Question ", tmp$variable)
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses_agree_disagree, above_mid="Somewhat Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy")

@@

responses <- c("Strongly Agree","Strongly Disagree") # response categories from top to bottom
tmp <- melt(d, measure.vars=paste0('Q_10_',1:11 ))
tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("10_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))

@@

tmp$variable <- letters[gsub("Q_", "", tmp$variable) %>% gsub("11_", "", .) %>% as.integer]
p <- plot_likert(tmp, response='value', var_x='label_PolicyAdoptedAtPublication_space', var_facet="variable", response_order=responses, above_mid="Strongly Agree", na.label="No response", xlab="% Responses", ylab="JDAP Policy", include.N=FALSE)
p <- p + theme(axis.text.x=element_text(angle=-90, size=8))
